\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2013-12-28 doc/paper.tex
briefly describe model parameter and beta function classes

\section{Stucture of the spectrum generator}
\subsection{boundary conditions}
Different types, how we match to low energy data.  reference EWSB or merge that section here.
mention two loop qcd parts from softsusy.
\subsection{RGEs}
The two loop renormalisation group equations are generated using command ?
Even in the simplest supersymmetric model the RGEs form a very large set of coupled non-linear differential equations.  To solve these and thereby evolve the parameters between two different scales \fs has... 
\subsection{tree level spectrum}
The diagonalised tree level $\overline{DR}$ masses are obtained from expressions...
The numerical diagonalisation is performed by... with an accuracy set by...   
\subsection{Electroweak symmetry breaking}
At tree level the EWSB conditions are written...
The one loop electroweak symmetry breaking are solved using the gsl routines finding multiple roots, \code{gsl_multiroot_fsolver}.  Iteration. For example in the MSSM \fs generates.. show code.
 If higher accuracy is required additional routines with higher order corrections can be added in a very simple way.  For example in the MSSM by default \fs adds two loop Higgs FORTRAN routines supplied by P.~Slavich from \cite{slavich-degrassi} to add two loop corrections of $\oatas$, $\oabas$, $\oatq$, $\oabatau$, 
$\oabq$, $\oatauq$ and $\oatab$  as follows...  
Something similar is done for the NMSSM, but in this case the NMSSM $\oatas$, $\oabas$ pieces come from \cite{Degrassi:2009yq}.
 Corrections from other sources can be added to the generated code by...
\subsection{two scale fixed point iteration}
The default solver which calls the above routines above and finds the full set of $\overline{DR}$ masses in the model consistent with all constraints is the two-scale solver.  This can be selected by... but if no selection is made this will be used anyway as default.

>>>>

\section{Stucture of the spectrum generator}
\subsection{boundary conditions}
Different types, how we match to low energy data.  reference EWSB or merge that section here.
mention two loop qcd parts from softsusy.

\subsection{Model parameters and RGEs}
Even in the simplest supersymmetric model the RGEs form a very large
set of coupled non-linear differential equations.  In a general
(softly broken) supersymmetric theory the soft-breaking parameters
depend on themselves and the susy parameters.  However, the susy
parameters are independent of the soft-breaking parameters [cite: MV,
Staub, Sperling].  This makes it possible to split the model
parameters and their into the following two subsets:
%
\begin{enumerate}
\item \emph{susy parameters:} gauge couplings, superpotential
  parameters and VEVs and
\item soft-breaking parameters.
\end{enumerate}
%
The susy parameters together with their two-loop renormalisation group
equations for the are stored in the class
\code{<model>_susy_parameters}.  The soft-breaking model parameters
together with their two-loop renormalisation group equations for the
are stored in the class \code{<model>_soft_parameters}.  The
dependence of the soft-breaking parameters on the susy parameters is
implemented via inheritance, see
\figurename~\ref{fig:parameter-classes}.
%
\begin{figure}
  \centering
  \tikzumlset{fill class=white}
  \begin{tikzpicture}
    \umlclass[x=0, y=3]{model\_susy\_parameters}{
      - susy parameters
    }{
      + beta()
    }
    \umlclass[x=0, y=0]{model\_soft\_parameters}{
      - soft-breaking parameters
    }{
      + beta()
    }
    \umlinherit{model\_soft\_parameters}{model\_susy\_parameters}
  \end{tikzpicture}
  \caption{Model parameter class structure.}
  \label{fig:parameter-classes}
\end{figure}

\subsection{tree level spectrum}
The diagonalised tree level $\overline{DR}$ masses are obtained from expressions...
The numerical diagonalisation is performed by... with an accuracy set by...   
\subsection{Electroweak symmetry breaking}
At tree level the EWSB conditions are written...
The one loop electroweak symmetry breaking are solved using the gsl routines finding multiple roots, \code{gsl_multiroot_fsolver}.  Iteration. For example in the MSSM \fs generates.. show code.
 If higher accuracy is required additional routines with higher order corrections can be added in a very simple way.  For example in the MSSM by default \fs adds two loop Higgs FORTRAN routines supplied by P.~Slavich from \cite{slavich-degrassi} to add two loop corrections of $\oatas$, $\oabas$, $\oatq$, $\oabatau$, 
$\oabq$, $\oatauq$ and $\oatab$  as follows...  
Something similar is done for the NMSSM, but in this case the NMSSM $\oatas$, $\oabas$ pieces come from \cite{Degrassi:2009yq}.
 Corrections from other sources can be added to the generated code by...
\subsection{two scale fixed point iteration}
The default solver which calls the above routines above and finds the full set of $\overline{DR}$ masses in the model consistent with all constraints is the two-scale solver.  This can be selected by... but if no selection is made this will be used anyway as default.
